---
title: "Project 2"
author: "Group 4"
date: "2023-10-08"
output: html_document
runtime: shiny
---

```{r imports, echo = FALSE, warning = FALSE, message = FALSE}
library(magrittr)
library(here)
library(stringr)
library(dplyr)
library(shiny)
library(ggplot2)
library(plotly)
library(RColorBrewer)
library(leaflet)
library(forcats)
library(leaflet.extras)
library(mapview)
library(leafsync)
library(ggvis)
library(shinydashboard)
library(lubridate)
library(pacman)
library(zipcodeR)
library(data.table)
library(devtools)
library(tigris)
library(htmltools)
library(rsconnect)
library(shinyWidgets)
```

Load in some helper functions to help download and load relevant data.
Ensure that your working directory is correctly set to the root of this project.
If this cell does not run, please navigate to the root directory and double click
`ADS-Fall2023-Project2-ShinyApp-Group4.Rproj`.
```{r load_files, echo = FALSE, warning = FALSE, message = FALSE}
source_files <- list.files(here("lib")) %>%
  str_subset("\\.R$") %>%
  str_c(here("lib"), "/", .)

lapply(source_files, source)
```

```{r load_data, warning = FALSE, message = FALSE}
download_data()
load_data()
```

Some basic preprocessing to grab only the relevant columns and rows.
```{r claim_amount_filter}
coastal_states <- c("ME", "NH", "MA", "RI", "CT", "NY", "NJ", "DE", "MD",
                    "VA", "NC", "SC", "GA", "FL", "AL", "MS", "LA", "TX",
                    "CA", "OR", "WA", "AK", "HI")

claim_amounts_df <- claims_df %>%
  dplyr::select(amountPaidOnBuildingClaim,
                amountPaidOnContentsClaim,
                amountPaidOnIncreasedCostOfComplianceClaim,
                totalBuildingInsuranceCoverage,
                totalContentsInsuranceCoverage,
                yearOfLoss,
                buildingDamageAmount,
                buildingDeductibleCode,
                netBuildingPaymentAmount,
                buildingPropertyValue,
                causeOfDamage,
                state
                ) %>%
  dplyr::filter(!rowSums(is.na(.)) > 0) %>%
  mutate(is_coastal = state %in% coastal_states,
         payment_exceeds_damage = amountPaidOnBuildingClaim >= buildingDamageAmount)
```

Adds all of the ui and server files for the shiny app.
Each individual component can be viewed in `/app`.
```{r load_app_files, echo = FALSE, warning = FALSE, message = FALSE}
setwd(here("app"))

source_files <- list.files(here("app")) %>%
  str_subset("\\.R$") %>%
  str_c(here("app"), "/", .)

lapply(source_files, source)
```
```{r run_app, echo = FALSE, warning = FALSE, message = FALSE}
shinyApp(ui = ui, server = server)
```